### 2017-04-06 paper/evaluation.tex
fixing rq3

Results indicate that, on average, parallel execution was
\avgSpeedup{} times faster compared to sequential execution.  We noted
two extreme cases: \CodeIn{Jcabi} and \CodeIn{Log4J2}.
The first when using the default parallel configuration, runs a
\textbf{C3} configuration with small test classes and big test
methods, allowing to run multiple methods and classes at once. The
high slowdown happens when big methods run sequentially.
\Comment{The second which most test
classes run one, two, or three test methods with the configuration
\Mar{We are not using bold for these.  If you want you can change, but
  please do so by holding all locks.}\textbf{C2}, without the
reutilization of JVM forks\Mar{Don't understand.
  Fork-configurations have an F in front, no?  Like FC1.  Please
  check.  Do you mean FC0 for Log4J? (I checked Figure 10)}. This specific
configuration is useful when there is the need to isolate the test
class execution from another, which is the case.}
\Luis{$\leftarrow$ rework this} \Fix{falar
  sobre o resultado geral dos speedups - elaborar menor e maior
  speedup... acho que so vale a pena discutir quando tiver conviccao
  dos 2 casos}

>>>>

Results indicate that, on average, parallel execution was
\avgSpeedup{} times faster compared to sequential execution.  We noted
two extreme cases: \CodeIn{Jcabi} and \CodeIn{Log4J2}.
The first when using the default parallel configuration, runs a
\textbf{C3} configuration with small test classes and big test
methods, allowing to run multiple methods and classes at once. The
high slowdown happens when big methods run sequentially.
The second when using the default parallel configuration, runs a
\textbf{FC0} configuration with small test classes and small test
methods, which is slowdown by the JVM creation overhead. This
configuration is useful to isolate each test method from each other.
\Luis{$\leftarrow$ rework this} \Fix{falar
  sobre o resultado geral dos speedups - elaborar menor e maior
  speedup... acho que so vale a pena discutir quando tiver conviccao
  dos 2 casos}
